Radiocarbon measurement of CO~2~ from carbonate minerals using a gas ion source with an open split interface

### 2021-10-21 doc/AMS-15/AMS-15_poster.Rmd
improve figure sizes, colors.

```{r cur-flow-os, fig.height=4, dev='svg'}
ggplot(data, aes(co2flow, he12C)) +
  geom_smooth(span = .3, se=FALSE, color = "#00b7bd") +
  geom_point(size = 3, color = "#0069b1") +
  labs(title = "Ion current is stable for a range of CO2 flow",
       subtitle = "Current vs. CO2 flow during vial dillution",
       x = bquote('CO'[2]~'Flow (μl/min)'), 
       y = "12C current (μA)") +
  theme_classic()
```

@@

```{r blanks, fig.height=4, dev='svg'}
cons_df %>% 
  filter(fm_consensus < 0.1) %>% 
  ggplot(aes(he12C, norm_ratio)) +
  geom_errorbar(aes(ymin = norm_ratio - sig_norm_ratio, ymax = norm_ratio  + sig_norm_ratio)) +
  geom_errorbarh(aes(xmin = he12C - sig_he12C, xmax = he12C  + sig_he12C)) +
  geom_point(aes(color = wheel), size = 3) +
  #scale_color_manual("wheel", values = c("#b7bf10", "#00a9e0", "#0069b1")) +
  labs(title = "Contaminant carbon is related to current",
       subtitle = "Fm and current of radiocarbon-free carbonates",
       x = "12C Current (μA)",
       y = "Fraction modern") +
  theme_classic() +
  theme(legend.position = c(0.82, 0.76),
        legend.background = element_rect(fill = "white", color = "black")) 
```

@@

@@

```{r, fig.height=5}
bc_gr <- plot(cal_dates_gr) +
  xlim(8000, 0) +
  ylim(1000, 0) +
  labs(title = "Graphite measurements",
       xlab = "Age (yBP)",
       ylab = "Core depth (cm)")

bc_gas <- plot(cal_dates_gas) +
  xlim(8000, 0) +
  ylim(1000, 0) +
  labs(title = "HGIS measurements",
       xlab = "Age (yBP)",
       ylab = "Core depth (cm)")

>>>>

```{r cur-flow-os}
ggplot(data, aes(co2flow, he12C)) +
  geom_smooth(span = .3, se=FALSE, color = "#00b7bd") +
  geom_point(size = 2, color = "#0069b1") +
  labs(title = "Ion current is stable for a range of CO2 flow",
       subtitle = "Current vs. CO2 flow during vial dillution",
       x = bquote('CO'[2]~'Flow (μl/min)'), 
       y = "12C current (μA)") +
  theme_classic()
```

@@

```{r blanks}
cons_df %>% 
  filter(fm_consensus < 0.1) %>% 
  ggplot(aes(he12C, norm_ratio)) +
  geom_errorbar(aes(ymin = norm_ratio - sig_norm_ratio, ymax = norm_ratio  + sig_norm_ratio)) +
  geom_errorbarh(aes(xmin = he12C - sig_he12C, xmax = he12C  + sig_he12C)) +
  geom_point(size = 2, color = "#0069b1") + #"#b7bf10"
  #scale_color_manual("wheel", values = c("#b7bf10", "#00a9e0", "#0069b1")) +
  labs(title = "Contaminant carbon is related to current",
       subtitle = "Fm and current of radiocarbon-free carbonates",
       x = "12C Current (μA)",
       y = "Fraction modern") +
  theme_classic() +
  theme(legend.position = c(0.82, 0.76),
        legend.background = element_rect(fill = "white", color = "black")) 
```

@@

<br><br>

@@

```{r, fig.height=5}
bc_gr <- plot(cal_dates_gr) +
  xlim(8000, 0) +
  ylim(1000, 0) +
  labs(title = "Graphite measurements",
       x = "Age (yBP)",
       y = "Core depth (cm)")

bc_gas <- plot(cal_dates_gas) +
  xlim(8000, 0) +
  ylim(1000, 0) +
  labs(title = "HGIS measurements",
       x = "Age (yBP)",
       y = "Core depth (cm)")
